Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Guideline for International Students

### 2024-01-27 demystify.tex
Updates from Overleaf

Finally, this is something easy to do, but is neglected by many
applicants: \textbf{customize the statement} for the school you're applying to,
e.g., why do you apply \emph{here}? provide names of professors who you're interested in (in many cases your application will be forwarded to them for evaluation).
This shows that you're serious and have done homework on places you're applying to.
Adcom will look for this part at the end of the statement, so do not skip it.

\begin{commentbox}[Vu:]
  I often read the research statement (and the LORs) first. If I am
  persuaded by then, I would skim over other factors and advocate for
  admission (unless I see red flags in other parts). If I am not
  convinced, then I will likely recommend rejection (unless I see
  something standout in other parts).
  \tcblower
  Do careful research on professors, don't mention \emph{emeritus} or  adjunct faculty.
  Also, be careful not to send statements to wrong schools or mixing
  facts (e.g., talking about school X but mentioned about working with
  profs. at school Y; and definitely do not talk about George Washington when applying to George Mason). I have seen such statements more time that I
  should.
\end{commentbox}

@@

Graduating from top universities \emph{that we recognize} helps. For example, if your school is well-known, then it is \emph{``top foreign''}, which is definitely a plus.
However, if committee members do not know much about schools in your country, they will likely treat your school as
\emph{``unknown foreign''}, which can be a minus point because we are uncertain about the quality of your school.

>>>>

Finally, this is something easy to do, but is neglected by many
applicants: \textbf{customize the statement} for the school you're applying to,
e.g., why do you apply \emph{here}? provide names of professors who you're interested in (if they are not already in the adcom, your application might get forwarded to them for evaluation; and they will likely be those who interview you).
This shows that you're serious and have done homework on places you're applying to.
Adcom will look for this part at the end of the statement, so do not skip it.

\begin{commentbox}[Vu:]
  I often read the research statement (and the LORs) first. If I am
  persuaded by then, I would skim over other factors and advocate for
  admission (unless I see red flags in other parts). If I am not
  convinced, then I will likely recommend rejection (unless I see
  something standout in other parts).
  \tcblower
  Do careful research on professors, don't mention \emph{emeritus} or  adjunct faculty (see more about various types of faculty in \S\ref{sec:faculty-types}).
  Also, be careful not to send statements to wrong schools or mixing
  facts (e.g., talking about school X but mentioned about working with
  profs. at school Y; and definitely do not talk about George Washington when applying to George Mason). I have seen such statements more time that I
  should.
\end{commentbox}

@@

Graduating from top universities \emph{that we recognize} helps. For example, if your school is well-known, then it is \emph{``top foreign''}, which is definitely a plus.
However, if committee members do not know much about schools in your country, they will likely treat your school as
\emph{``unknown foreign''}, which can be a minus point because they are uncertain about the quality of your school.
